$Z^\prime$ mass limits and the naturalness of supersymmetry

### 2015-02-24 paper/e6ssm-tuning-paper.tex
Removed undefined reference
Simplified and added O(t^2) contribution to the series expansion of lambda
Factorised a term in the 2-loop beta function for lambda, added a missing label
Started adding beta functions and O(t^2) coefficient for A_\lambda

In addition to this, the soft parameters in E$_6$SSM BM2 follow a pattern similar to that found in the constrained
model. With the exception of the parameters $m_{Q3}^2$, 
$m_{u3}^2$, $m_{H_d}^2$, $m_{H_u}^2$, and $M_3$, the values of which are given in Table \ref{tab:benchmarks}, 
the soft masses at the SUSY scale correspond to the values that result in the cE$_6$SSM with $m_0=2.2$ TeV, 
$M_{1/2}=1003$ GeV, $A_0=500$ GeV, $\kappa_{1,2,3}(M_X)=0.1923$, $\lambda(M_X)=0.2646$ and
$\lambda_{1,2}(M_X)=0.1$. This leads to a significant reduction in the contributions to the RG running of $m_{H_u}^2$ and $m_{Q3}^2$ coming from terms of the form $g_1^2\Sigma_1$ and, to a lesser extent, $g_1'^2\Sigma_1'$. Here we define (see also Eq.~(\ref{}))
\begin{align*}
\Sigma_1&=\sum_{i=1}^3\left ( m_{Qi}^2-2m_{ui}^2+m_{di}^2+m_{ei}^2-m_{Li}^2+m_{H_{ui}}^2-m_{H_{di}}^2+m_{\overline{D}_i}^2-m_{Di}^2\right )-m_{H'}^2+m_{\overline{H'}}^2,\\
\Sigma_1'&=\sum_{i=1}^3\left ( 6m_{Qi}^2+3m_{ui}^2+6m_{di}^2+m_{ei}^2+4m_{Li}^2-4m_{H_{ui}}^2-6m_{H_{di}}^2+5m_{Si}^2-9m_{\overline{D}_i}^2-6m_{Di}^2\right )\\
&\quad{}+4m_{H'}^2-4m_{\overline{H'}}^2.
\end{align*}
In the unconstrained case, this contribution acts to drive up the values of $m_{Q3}^2$ and $m_{H_u}^2$, and thus the associated tuning sensitivities, at the cutoff scale $M_X$. In the case of E$_6$SSM BM2, on the other hand, the reduced splitting between the soft masses leads to a much smaller contribution from these terms. Together with the reduction in $M_3$ described above, this allows to maintain the observed low fine tuning at very large values of $M_X$.

@@

In order to keep our expressions compact we have used the notation

@@

Note that in these expressions the $U(1)_Y$ and $U(1)'$ charges are assumed to be GUT-normalised. Similarly we have set
\Sigma_\lambda=\lambda_1^2+\lambda_2^2+\lambda_3^2, \qquad \Sigma_\kappa=\kappa_1^2+\kappa_2^2+\kappa_3^2.

@@

are

@@

&{} -3\left ( 3y_t^4+3y_b^4+2y_t^2y_b^2+y_\tau^2 \right )+6g_2^2\Sigma_\lambda+g_1^2\left ( \frac{4}{5}y_t^2-\frac{2}{5}y_b^2+\frac{6}{5}y_\tau^2+\frac{4}{5}\Sigma_\kappa +\frac{6}{5}\Sigma_\lambda\right )\nonumber\\

@@

&{}+\frac{9}{5}g_1^2g_2^2+6g_1'^2g_2^2\left ( \tilde{Q}_1^2+\tilde{Q}_2^2\right )+\frac{6}{5}g_1^2g_1'^2\left [\tilde{Q}_1^2+\tilde{Q}_2^2+\left ( \tilde{Q}_2-\tilde{Q}_1\right )\Sigma_{\tilde{Q}}^Y\right ]\bigg \}.\label{eq:USSMLambdaBetaTwoLoop}

>>>>

In addition to this, the soft parameters in E$_6$SSM BM2 follow a pattern similar to that found in the constrained
model. With the exception of the parameters $m_{Q3}^2$, 
$m_{u3}^2$, $m_{H_d}^2$, $m_{H_u}^2$, and $M_3$, the values of which are given in Table \ref{tab:benchmarks}, 
the soft masses at the SUSY scale correspond to the values that result in the cE$_6$SSM with $m_0=2.2$ TeV, 
$M_{1/2}=1003$ GeV, $A_0=500$ GeV, $\kappa_{1,2,3}(M_X)=0.1923$, $\lambda(M_X)=0.2646$ and
$\lambda_{1,2}(M_X)=0.1$. This leads to a significant reduction in the contributions to the RG running of $m_{H_u}^2$ and $m_{Q3}^2$ coming from terms of the form $g_1^2\Sigma_1$ and, to a lesser extent, $g_1'^2\Sigma_1'$. Here we define
\begin{align*}
\Sigma_1&=\sum_{i=1}^3\left ( m_{Qi}^2-2m_{ui}^2+m_{di}^2+m_{ei}^2-m_{Li}^2+m_{H_{ui}}^2-m_{H_{di}}^2+m_{\overline{D}_i}^2-m_{Di}^2\right )-m_{H'}^2+m_{\overline{H'}}^2,\\
\Sigma_1'&=\sum_{i=1}^3\left ( 6m_{Qi}^2+3m_{ui}^2+6m_{di}^2+m_{ei}^2+4m_{Li}^2-4m_{H_{ui}}^2-6m_{H_{di}}^2+5m_{Si}^2-9m_{\overline{D}_i}^2-6m_{Di}^2\right )\\
&\quad{}+4m_{H'}^2-4m_{\overline{H'}}^2.
\end{align*}
In the unconstrained case, this contribution acts to drive up the values of $m_{Q3}^2$ and $m_{H_u}^2$, and thus the associated tuning sensitivities, at the cutoff scale $M_X$. In the case of E$_6$SSM BM2, on the other hand, the reduced splitting between the soft masses leads to a much smaller contribution from these terms. Together with the reduction in $M_3$ described above, this allows to maintain the observed low fine tuning at very large values of $M_X$.

@@

In order to keep these expressions compact we have used the notation

@@

Note that in these expressions the $U(1)_Y$ and $U(1)'$ charges are assumed to be GUT-normalised. Similarly we will write
&\Sigma_\lambda=\lambda_1^2+\lambda_2^2+\lambda_3^2, \qquad \Sigma_\kappa=\kappa_1^2+\kappa_2^2+\kappa_3^2,\\
&\Pi_\lambda=\lambda_1^4+\lambda_2^4+\lambda_3^4,\qquad \Pi_\kappa=\kappa_1^4+\kappa_2^4+\kappa_3^4.

@@

and the $O(t^2)$ coefficient in the series expansion are

@@

&{} -3\left ( 3y_t^4+3y_b^4+2y_t^2y_b^2+y_\tau^2 \right )+6g_2^2\Sigma_\lambda+\frac{2}{5}g_1^2\left ( 2y_t^2-y_b^2+3y_\tau^2+2\Sigma_\kappa +3\Sigma_\lambda\right )\nonumber\\

@@

&{}+\frac{9}{5}g_1^2g_2^2+6g_1'^2g_2^2\left ( \tilde{Q}_1^2+\tilde{Q}_2^2\right )+\frac{6}{5}g_1^2g_1'^2\left [\tilde{Q}_1^2+\tilde{Q}_2^2+\left ( \tilde{Q}_2-\tilde{Q}_1\right )\Sigma_{\tilde{Q}}^Y\right ]\bigg \},\label{eq:USSMLambdaBetaTwoLoop}\\
b_\lambda^{(2)}&=\lambda \bigg \{ 2\lambda^2\left ( 3\lambda^2 +4\Sigma_\lambda +6\Sigma_\kappa \right )+4\Pi_\lambda + 6\Pi_\kappa +6\left ( \Sigma_\lambda+\frac{3}{2}\Sigma_\kappa\right )^2+7\lambda^2\left ( 3y_t^2+3y_b^2+y_\tau^2\right )\nonumber\\
&{}+\left ( 3y_t^2+3y_b^2+y_\tau^2\right )\left (2\Sigma_\lambda+3\Sigma_\kappa\right ) +3\left ( \frac{15}{2}y_t^4+\frac{15}{2}y_b^4+\frac{3}{2}y_\tau^4 +5y_b^2y_t^2 +3y_b^2y_\tau^2 +y_t^2y_\tau^2\right )\nonumber\\
&{}-\frac{1}{5}g_1^2\left ( 12\lambda^2+16y_b^2+22y_t^2+12y_\tau^2+12\Sigma_\lambda +13\Sigma_\kappa \right )\nonumber\\
&{}-3g_2^2\left ( 4\lambda^2+6y_t^2+6y_b^2+2y_\tau^2+4\Sigma_\lambda+3\Sigma_\kappa\right )-16g_3^2\left ( y_t^2+y_b^2+\Sigma_\kappa \right )\nonumber\\
&{}-2g_1'^2\left [ 4\left ( \tilde{Q}_1^2+\tilde{Q}_2^2+\tilde{Q}_S^2\right )\left ( \lambda^2 +\Sigma_\lambda \right )+3\Sigma_\kappa\left ( \tilde{Q}_1^2+\tilde{Q}_2^2+\tilde{Q}_S^2+\tilde{Q}_D^2+\tilde{Q}_{\overline{D}}^2\right )\right .\nonumber\\
&{}+3y_b^2\left ( 2\tilde{Q}_1^2+\tilde{Q}_2^2+\tilde{Q}_d^2+\tilde{Q}_Q^2+\tilde{Q}_S^2 \right )+3y_t^2\left ( \tilde{Q}_1^2+2\tilde{Q}_2^2+\tilde{Q}_Q^2+\tilde{Q}_S^2+\tilde{Q}_u^2\right )\nonumber\\
&{}\left.+y_\tau^2\left ( 2\tilde{Q}_1^2+\tilde{Q}_2^2+\tilde{Q}_e^2+\tilde{Q}_L^2+\tilde{Q}_S^2\right )\right ]-\frac{15}{2}g_2^4-\frac{279}{50}g_1^4\nonumber\\
&{}+2g_1'^4\left ( \tilde{Q}_1^2+\tilde{Q}_2^2+\tilde{Q}_S^2 \right )\left (\tilde{Q}_1^2+\tilde{Q}_2^2+\tilde{Q}_S^2-\Sigma_{\tilde{Q}}\right )+\frac{9}{5}g_1^2g_2^2+6g_1'^2g_2^2\left ( \tilde{Q}_1^2+\tilde{Q}_2^2+\tilde{Q}_S^2\right )\nonumber\\
&{}+\frac{6}{5}g_1^2g_1'^2\left ( \tilde{Q}_1^2+\tilde{Q}_2^2+\tilde{Q}_S^2 \right ) \bigg \}.\label{eq:USSMLambdaOt2Coeff}
It is sufficient to consider the trilinear coupling $a_\lambda\equiv \lambda A_\lambda$, for which the relevant expressions read
\begin{subequations}
\beta_{a_\lambda}^{(1)}&=,\label{eq:USSMTLambdaBetaOneLoop}\\
\beta_{a_\lambda}^{(2)}&=,\label{eq:USSMTLambdaBetaTwoLoop}\\
b_{a_\lambda}^{(2)}&=.\label{eq:USSMTLambdaOt2Coeff}
